jInfer Architecture

### 2010-09-18 doc/jInfer/Architecture.tex
Documentation: Architecture: work in progress.

The classes that represent XML elements, attributes and simple text data are summarized in figure \ref{img-arch-nodes}.

\begin{figure}
	\includegraphics[scale=0.3]{Architecture-images/nodes.eps} 
	\caption{UML class diagram of classes representing parts of XML}
	\label{img-arch-nodes}
\end{figure}

It is important to note that attributes in jInfer's data structures are nodes, just like elements and simple data.\\

Description of all classes from the schema follows.

\subsubsection{AbstractNode}

\subsubsection{Element}

\subsubsection{AbstractContentNode}

\subsubsection{Attribute}

\subsubsection{SimpleData}

>>>>

The classes that represent XML elements, attributes and simple text data (collectively known as \textit{XML nodes}) are summarized in figure \ref{img-arch-nodes}.

\begin{figure}
	\includegraphics[scale=0.3]{Architecture-images/nodes.eps} 
	\caption{UML class diagram of classes representing XML nodes}
	\label{img-arch-nodes}
\end{figure}

It is important to note that attributes in jInfer's data structures are nodes too, just like elements and simple data.\\

Description of all classes from the schema follows. All classes can be found in \texttt{cz.cuni.mff.ksi.jinfer.base.objects} package.

\subsubsection{\texttt{NodeType}}

NodeType is an enum of all non-abstract node types, i.e. ATTRIBUTE, ELEMENT, SIMPLE\_DATA.

\subsubsection{\texttt{AbstractNode}}

A common ancestor of all XML nodes. Contains the following members:
\begin{itemize}
	\item \texttt{context} - a list of \texttt{String}s, element names, marking the path from this document's root element to the current node. For example, in a document like this
\begin{verbatim}
<people>
<person>
<name first="John" last="Doe">
</person>
</people>
\end{verbatim} % TODO tabs
the element \texttt{$<$name$>$} would have context \texttt{\{"people", "person"\}} while the element \texttt{$<$people$>$} would have an empty list for context.
	\item \texttt{name} - a String representing this node's name. For \texttt{ELEMENT}s and \texttt{ATTRIBUTES}s this is their name. For \texttt{SIMPLE\_DATA}, this is the string representation of the textual data in this node.
	\item \texttt{metadata} - a map indexed by \texttt{String}s, containing general \texttt{Object}s containing various metadata related to this node. At this moment, three types of metadata are recognized:
	\begin{itemize}
		\item required - used in \texttt{ATTRIBUTE}s. If there is a \texttt{Boolean.TRUE} value under this key in metadata, it means that the attribute represented by this node is considered to be required (for example, in DTD this would be marked as \texttt{\#REQUIRED}).
		\item \texttt{from.schema} - a \texttt{Boolean.TRUE} value under this key means that this node was obtained while processing an XML schema.
		\item \texttt{from.query} - a \texttt{Boolean.TRUE} value under this key means that this node was obtained while processing a query.
	\end{itemize}
	jInfer module are free to ignore or process these metadata.
\end{itemize}
Method \texttt{getType()} returning this node's \texttt{NodeType} is declared as abstract and overriden in corresponding classes.

\subsubsection{\texttt{Element}}

Represents an actual XML element. Apart from the members mentioned before, a new member \texttt{subnodes} is introduced. \texttt{subnodes} is of type \texttt{Regexp$<$AbstractNodes$>$}. This regular expression describes the allowed content of this node (i.e. the nodes that can be within, hence \textit{subnodes}). \texttt{subnodes} may be \texttt{null}.

\subsubsection{\texttt{AbstractContentNode}}

A common ancestor for nodes that have some (usually textual) content. This class is generic, however, this document assumes it to be parametrized as \texttt{AbstractContentNode$<$String$>$} for the sake of simplicity. Contains the following members:
\begin{itemize}
	\item \texttt{contentType} - a \texttt{String} describing the type of the content in this node. Note that the parameter is currently ignored and will probably be deleted or changed.
	\item \texttt{content} - a list of \texttt{String}s holding the actual content of this node. Note that a single node has only one string as its content, however, as the nodes are routinely aggregated, this list might hold all the contents of the original aggregated nodes.
\end{itemize}

\subsubsection{\texttt{Attribute}}

This is just a marker implementation of an \texttt{AbstractContentNode$<$String$>$}. Represents an XML attribute.

\subsubsection{\texttt{SimpleData}}

This is just a marker implementation of an \texttt{AbstractContentNode$<$String$>$}. Represents XML simple text data.
